\documentclass{article}

\input{resume_format}

\begin{document} 
\title{Shih-Hao Tseng}{
503 Summerhill Drive Apt.4\\
Ithaca, NY 14850 \\
U.S.A.
}{
(607) 280-7864 (Mobile) \\
st688@cornell.edu
}

\section{Education}
\subsection{Cornell University (CU)}{Ithaca, NY, U.S.A.}{Aug. 2013 - Present}
\content{
\position{PhD student (Advisor: Dr. Kevin Tang, major in Electrical and Computer Engineering)}
\bulletitem{Relevant Coursework: \\
\hspace*{0.5cm} Practicum in Operating Systems, Approximation Algorithm, Convex Analysis, Functional Analysis, Statistical Inference and Decision, Stochastic Systems: Estimation and Control.}
}
\vspace*{0.1in}

\subsection{National Taiwan University (NTU)}{Taipei, Taiwan}{Sep. 2008 - June 2012}
\content{
\position{Bachelor of Science in Engineering (minor in Economics)}
\bulletitem{GPA: 92.20/100.00; ranking $2^{\rm nd}$ in a class of 226}
\bulletitem{Relevant Coursework: \\
\hspace*{0.5cm}Algorithm, Data Structure and Programming, Rf Microwave Wireless Systems, Signals and Systems, Advanced Calculus, Macroeconomics, Microeconomics, Probability and Statistics, Quantum Physics.}
}\vspace*{0.1cm}

\section{Research Interests}
\content{
\bolditem{Software-Defined Networking}{}
\bulletitem{Centralized control, congestion-free routing and high-frequency network updating.}
\bolditem{Communication System}{}
\bulletitem{Network dynamic model, optimization theory and algorithm.}
}\vspace*{0.1cm}

\section{Publications}
\content{
\nocite{*}
\bibliographystyle{resume_bst}
\bibliography{resume_bib}
}\vspace*{0.1cm}

\section{Honors and Awards}
\subsection{Winner of the AT\&T SDN Network Design Challenge}{}{2016}
\content{
\bulletitem{Awarded to the top team providing the most efficient and cost effective routing method.}
}\\[-1pt]
\subsection{Jacobs Fellowship (CU)}{}{2014}
\subsection{Studying Abroad Scholarship (Ministry of Education, Taiwan(R.O.C.))}{}{2013}
\subsection{Honorary Member of the Phi Tau Phi Scholastic Honor Society}{}{2012}
\content{
\bulletitem{Presented to seniors from each college in Taiwan ranking within top 1\% of their department.}
}\\[-1pt]
\subsection{President's Awards (NTU)}{}{2009, 2010, 2011, 2012}
\content{
\bulletitem{Four-time recipient; awarded to students ranking within top 5\% of their department.}
}\\[-1pt]
\subsection{Outstanding Project Award}{}{2011}
\content{
\bulletitem{Awarded to the top 10 teams of Cross-Strait Finals of 2011 Innovate Asia Competition (FPGA design).}
}
%\subsection{Freshman Chinese Writing Award (NTU)}{}{2009}
\vspace*{0.1cm}

\section{Skills}
\content{
\bolditem{Programming Languages:}{Proficient in C++, Python and Verilog; working knowledge of ActionScript, C, Basic, HTML, Java, JavaScript, MySQL, and PHP.}
\bolditem{Simulation Tools:}{Proficient in PSpice, MATLAB, and NS-3.}
\bolditem{Languages:}{Fluent in English; native in Mandarin Chinese and Taiwanese Hokkien; basic understanding of French, German, Spanish, and Japanese.}
}\vspace*{0.1cm}

\section{Experience}
\subsection{Cornell University}{Ithaca, NY, U.S.A.}{Aug. 2014  - Present}
\content{
\position{Graduate Research Assistant/Teaching Assistant}
\bulletitem{Developed a virtual SDN test framework to verify congestion-free updating properties.}
\bulletitem{Helped teach Introduction to Probability and Inference for Random Signals and Systems.}
}\\
\subsection{The Chinese University of Hong Kong}{Shatin, NT, Hong Kong}{June 2017  - Aug. 2017}
\content{
\position{Research Assistant}
\bulletitem{Developed efficient scheduling algorithms for hybrid packet/circuit networks.}
}\\
\subsection{AT\&T}{Middletown, NJ, U.S.A.}{June 2016  - Aug. 2016}
\content{
\position{Student Intern - Technical II}
\bulletitem{Developed models and designed algorithms for hybrid software-defined networks.}
}

\iffalse
\subsection{Army, Republic of China Armed Forces}{Taipei, Taiwan}{Aug. 2012  - July 2013}
\content{
\position{Chief Counselor, Second Lieutenant}
\bulletitem{Chief political warfare manager of a company.}
}\vspace*{0.1cm}
\fi

\iffalse
\section{Leadership and Activities}
\subsection{Cornell Taiwanese Student Association (CTSA)}{Webmaster}{May 2014 - Present}
\subsection{National Experimental High School at Hsinchu Science Park (NEHS) Alumni Association}{Founding Member and Director of Information Division}{Oct. 2010 - July 2012}
\subsection{NTU Electrical Engineering Summer Camp}{Instructor of Programming Languages and Director of Education}{2009, 2010, 2011}
\fi

\end{document}