\section{Experience}
\subsection{Meta Platforms, Inc.}{Menlo Park, CA, U.S.A.}{Dec. 2021 - Present}
\content{
\position{Research Scientist}
}\\[0.1in]
\subsection{California Institute of Technology}{Pasadena, CA, U.S.A.}{Oct. 2018 - Oct. 2021}
\content{
\position{Postdoctoral Scholar Research Associate}
\bulletitem{Led the project of freshness-driven network control.}
\bulletitem{Mentored graduate students on parallel model predictive control and formal test-case generation.}
\bulletitem{Derived realization-stability lemma that unifies existing controller synthesis methods.}
\bulletitem{Investigated the controller deployment architecture for cyber-physical systems.}
\bulletitem{Developed efficient computation technique via dynamic programming and flexible Python framework for system level synthesis.}
}\\[0.1in]
\subsection{Cornell University}{Ithaca, NY, U.S.A.}{Aug. 2014 - Aug. 2018}
\content{
\position{Graduate Research Assistant/Teaching Assistant}
\bulletitem{Built CodedBulk to boost the throughput of inter-datacenter bulk transfers using network coding.}
\bulletitem{Studied time-aware network management under software-defined networking.}
\bulletitem{Helped teach Introduction to Probability and Inference for Random Signals and Systems.}
}\\[0.1in]
\subsection{The Chinese University of Hong Kong}{Shatin, NT, Hong Kong}{June 2017 - Aug. 2017}
\content{
\position{Research Assistant}
\bulletitem{Developed efficient scheduling algorithms for hybrid packet/circuit networks.}
}\\[0.1in]
\subsection{AT\&T}{Middletown, NJ, U.S.A.}{June 2016  - Aug. 2016}
\content{
\position{Student Intern - Technical II}
\bulletitem{Developed routing algorithms to stabilize carrier-grade hybrid software-defined networks.}
}
\vspace*{0.1cm}

\iffalse
\subsection{Army, Republic of China Armed Forces}{Taipei, Taiwan}{Aug. 2012  - July 2013}
\content{
\position{Chief Counselor, Second Lieutenant}
\bulletitem{Chief political warfare manager of a company.}
}\vspace*{0.1cm}
\fi